Hydras \& Co.

### 2023-06-26 doc/chapter-fol.tex
small changes in documentation

\begin{remark}
  The function \texttt{close} applies \texttt{freeVarF} and
  \texttt{List.nodup}  in order to add a sequence of universal
  quantifications \texttt{allH $i_1$ \dots $i_k$}, in an order determined by the implementation of these functions. It may be interesting to check whether the proof of properties of \texttt{close} depend or not from this implementation.
\end{remark}
% \subsubsection{Computing a fresh variable}

@@

Let us for instance have a look  at \texttt{Formula\_depth\_ind2}. Its application in order to prove $P\;a$ generates 5 sub-goals.

@@

\begin{itemize}
\item Goals $1$ to $4$ correspond to  usual proofs by structural induction.
\item Goal $5$ is associated with a universal quantification $f=\forall\,v,a$. In this case, we have to prove that $P\;b$ holds for any formula $b$ which has a depth strictly less than $f$. Such a $b$ may for instance the result of replacing the free occurrences of $v$ in $a$ with any term $t$.
  \begin{todo}
   Make a link to an appropriate example.
  \end{todo}
\end{itemize}

\subsection{Free variables and substitutions}

>>>>

\begin{remark}
  The function \texttt{close} applies \texttt{freeVarF} and
  \texttt{List.nodup}  in order to add a sequence of universal
  quantifications \texttt{allH $i_1\, \dots\, i_k$}, in an order determined by the implementation of these functions. It may be interesting to check whether the proof of properties of \texttt{close} depend or not from this implementation.
\end{remark}
% \subsubsection{Computing a fresh variable}

@@

Let us for instance have a look  at \texttt{Formula\_depth\_ind2} which helps  to prove a goal $(P\;a)$ by generating five sub-goals.

@@

\begin{itemize}
\item Goals $1$ to $4$ correspond to  usual proofs by structural induction (without refering to \texttt{depth}).
\item Goal $5$ is associated with a universal quantification $f=\forall\,v,a$. In this case, we have to prove that $P\;b$ holds for any formula $b$ which has a depth strictly less than $f$. Such a $b$ may for instance be the result of replacing the free occurrences of $v$ in $a$ with any term $t$.

  \begin{todo}
   Make a link to an appropriate example.
  \end{todo}
\end{itemize}

\subsection{A correct definition of substF}

Substitution of a term to (free- occurrences of a variable 
in a formula is defined in a section of \href{../theories/html/hydras.Ackermann.folProp.html}{Ackermann.folProp}.
The definition itself takes 200 lines of \coq code, so we will only comment the \emph{structure} of this definition.

Fortunately, the reader may skip a few complex definitions 
(often because of dependent pattern matching), whose purpose
is twofold:
\begin{itemize}
\item Ensure that the substitution in a formula $F$ of a term $t$ to a variable $x$ returns a formula of the same depth as $F$,
  which allows to define a function by well-founded recursion on depth.
  \inputsnippets{folProp/substFHelp, folProp/substFDef}
\item Prove a few \emph{equations} which will be used in firther proofs on substitutions.

\inputsnippets{folProp/subFormulaEqual}
\inputsnippets{folProp/subFormulaRelation}
\inputsnippets{folProp/subFormulaImp}
\inputsnippets{folProp/subFormulaNot}
\inputsnippets{folProp/subFormulaForall}

\item Similar equations are also proved for derived connectors and quantifiers, for instance:

\inputsnippets{folProp/subFormulaAnd}
\inputsnippets{folProp/subFormulaExist}

\end{itemize}

\begin{project}
  Is it possible to get a more readable definition of \texttt{substF} using the \emph{Equations} plug-in~\cite{sozeau:hal-01671777} ? 
\end{project}

### 2023-06-26 doc/schutte-chapter.tex
small changes in documentation

Finally, we prove that \texttt{inject} is a bijection from the set of all terms of \texttt{T1} in normal form to the set 
\texttt{members epsilon0} of the elements of \texttt{Ord} strictly less than  $\epsilon_0$.

@@

\subsection{Remarks}
Let us recall that the library \href{../theories/html/hydras.Schutte.Schutte.html}%
{\texttt{Schutte}} depends on five \emph{axioms} and lies explicitly in the  
framework of classical logic with a weak version of the axiom of choice
(please look at the documentation of
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Logic.ChoiceFacts.html}{\texttt{Coq.Logic.ChoiceFacts}}).
Nevertheless, the other modules:
\href{../theories/html/hydras.Epsilon0.Epsilon0.html}%
{\texttt{Epsilon0}},
\href{../theories/html/hydras.Hydra.Hydra.html}%
{\texttt{Hydra}}, et 
\href{../theories/html/hydras.Gamma0.Gamma0.html}%
{\texttt{Gamma0}}
do not import any axioms and are really constructive.

>>>>

Finally, we prove that \texttt{inject} is a bijection from the set of all terms of \texttt{T1} in normal form to the set 
(\texttt{members epsilon0}) of the elements of \texttt{Ord} strictly less than  $\epsilon_0$.

@@

\subsection{Remarks}
Let us recall that the library \href{../theories/html/hydras.Schutte.Schutte.html}%
{\texttt{Schutte}} depends on five \emph{axioms} and lies explicitly in the  
framework of classical logic with a weak version of the axiom of choice
(please look at the documentation of
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Logic.ChoiceFacts.html}{\texttt{Coq.Logic.ChoiceFacts}}).

On the other hand, the other libraries:
\href{../theories/html/hydras.Epsilon0.Epsilon0.html}%
{\texttt{Epsilon0}},
\href{../theories/html/hydras.Hydra.Hydra.html}%
{\texttt{Hydra}}, et 
\href{../theories/html/hydras.Gamma0.Gamma0.html}%
{\texttt{Gamma0}}
do not import any axioms and are really constructive.
